Testing Quasar Unification with Clumpy Wind Models

### 2015-11-10 paper.tex
edited python intro

For this study, we use the MCRT code \py\  we have developed to carry out our radiative transfer and photoionization
calculations in non-local thermodynamic equilibrium (non-LTE) in a variety of disk-wind systems. 
We have used the code  to model accreting white dwarfs 
(Long \& Knigge 2002, hereafter LK02; Noebauer et al. 2010; 
Matthews et al. 2015, hereafter M15), young-stellar objects \citep{simmacro2005}
and quasars (H13).\nocite{noebauer, M15, LK02}  LK02 provides the basic description of the original code; improvements, see especially H14 and M15, have been described in subsequent reports.  A full description of the code will be published elsewhere; here we focus on the changes made to improve the ionization calculation and to allow for clumping in the wind.
%These studies contain extensive detail on the code,  so we only briefly describe the key elements of the global ionization calculation and other important aspects.

{\bf ksl - I a a bit torn over whether we add a few 3 sentences to describe the basic idea.  Some will be reading this for the first time.  Items that one would include are that we calculate the radiative transfer in a cylindrical coordinate system of dimension ?? x ??.  We have ionization and spectral cycles. In each cycle, ?? photon bundles are generated. We stop the ionization cycles after they converge, without any details.  I think this would be useful because we introduce terms like ``cell'' later on.', and without some kind of description they have no context}

>>>>

For this study, we use the MCRT code \py\ we have developed to carry out our 
radiative transfer and photoionization calculations in non-local thermodynamic 
equilibrium (non-LTE) in a variety of disk-wind systems. 
The code has been used to model accreting white dwarfs 
(Long \& Knigge 2002, hereafter LK02; Noebauer et al. 2010; 
Matthews et al. 2015, hereafter M15), young-stellar objects \citep{simmacro2005}
and quasars (H13).\nocite{noebauer, M15, LK02}  
The basic premise involves generating photons from an accretion disc
and central object, and computing their radiative transfer through an outflow.
This outflow is discretized into $n_x \times n_z$ cells in a 2.5D
cylindrical geometry with azimuthal symmetry.
First, the code gradually converges on a global temperature and ionization structure.
Once these ``ionization cycles'' are complete, then a series of further iterations
are completed to obtain a detailed synthetic spectrum.
LK02 provides the basic description of the original code; improvements, 
see especially H14 and M15, have been described in subsequent reports.  
%A full description of the code will be published elsewhere; 
Therefore we focus here on the changes made to improve the ionization calculation 
and to allow for clumping in the wind.
%These studies contain extensive detail on the code,  so we only briefly describe the key elements of the global ionization calculation and other important aspects.

% {\bf ksl - I a a bit torn over whether we add a few 3 sentences to describe the basic idea.  Some will be reading this for the first time.  Items that one would include are that we calculate the radiative transfer in a cylindrical coordinate system of dimension ?? x ??.  We have ionization and spectral cycles. In each cycle, ?? photon bundles are generated. We stop the ionization cycles after they converge, without any details.  I think this would be useful because we introduce terms like ``cell'' later on.', and without some kind of description they have no context}
